SPARQL on the Open, Decentralised Web

### 2016-07-29 dissertation/conclusions.tex
Some todos; mention that analysers are important
More future work

@@

Problems~\ref{prob:unknowndist},~\ref{prob:unknownconddist}~and~\ref{prob:largestats}
has a promising approach in \cite{5767868}.

>>>>

In Section~\ref{sec:understandquery}, it is noted that
Problem~\ref{prob:microcontroller} makes it important for a query
planner that integrates LDF query answering to find a balance between
client and server capability.

The lack of a formalisation of the notion of a useful cache entry is
noted in Section~\ref{sec:analpre}, and while there has been some work
on this topic, I am not aware of any attempt to do so in the context
of the present topic.

@@

Problems~\ref{prob:unknowndist},~\ref{prob:unknownconddist}~and~\ref{prob:largestats}
has a promising approach in \cite{5767868}, but a way to expose this
information to a client or a proxy is lacking. We saw in
\cite{splendid} that a VoID description can be used with some success,
but this needs further elaboration.
